### 2019-09-04 experiments.tex
work on some issues
12 hour change

Using TSTL's harness for {\tt redis-py}, both {\tt redis-py} and Redis
itself can be tested; unfortunately, generating stand-alone
high-coverage regression tests for {\tt redis-py} and Redis using TSTL
has proven difficult, as numerous Redis commands introduce nondeterministic
behavior:  thus the resulting tests are very often \emph{flaky}.   Using {\tt tstl\_afl\_fuzz}, we can see that the {\tt redis-py} has a 
stability of only 56.26\%, a clear indicator of nondeterminism. Some
of the problematic commands are obvious simply by inspection (e.g.,
{\tt randomkey, srandmember}).  And, given an understanding of Redis
semantics, it is also clear that the various
commands producing data with a limited lifetime (e.g., {\tt expire,
  pexpire}) also introduce timing-based nondeterminism.

@@

Using the original TSTL harness, just over 20\% of all {\tt redis-py}
regression tests (of length 200) generated were flaky.  Using the
nondeterminism checker to reduce flaky tests to a minimal set allows
us to simply set up an overnight run that will, in 12 hours, produce
a set of minimal flaky tests exposing the sources of
nondeterminism/flakiness.  In this case, the probability of flakiness
is not important, just the possibility, so we let the delta-debugging
create a minimal test with some non-zero (but possibly very small)
observed probability of nondeterminism.

>>>>

Using TSTL's harness for {\tt redis-py}, both {\tt redis-py} and Redis
itself can be tested; unfortunately, generating stand-alone
high-coverage regression tests for {\tt redis-py} and Redis using TSTL
has proven difficult, as numerous Redis commands introduce nondeterministic
behavior:  thus the resulting tests are very often \emph{flaky}.   Using {\tt tstl\_afl\_fuzz}, we can see that {\tt redis-py} has a 
stability of only 56.26\%, a clear indicator of nondeterminism. Some
of the problematic commands are obvious simply by inspection (e.g.,
{\tt randomkey, srandmember}).  And, given an understanding of Redis
semantics, it is also clear that the various
commands producing data with a limited lifetime (e.g., {\tt expire,
  pexpire}) also introduce timing-based nondeterminism.

@@

Using the original TSTL harness, just over 20\% of all {\tt redis-py}
regression tests (of length 200) generated were flaky.  Using the
nondeterminism checker to reduce flaky tests to a minimal set allows
us to simply set up an overnight run that will, in 12 hours, produce
a set of minimal nondeterministic tests exposing the sources of
nondeterminism/flakiness.  This process is unlikely to require 12
hours, of course; our point is that it is completely automated,
including generation of a set of minimal, distinct, tests showing
different kinds of nondeterminism using test normalization~\cite{onetest}.  The actual amount of time given
may be smaller, or, for that matter, larger (leaving an important
library to self-document nondeterminism over a weekend is hardly a bad
practice).  In this case, the probability of flakiness
is not important, just the possibility, so we let the delta-debugging
create a minimal test with some non-zero (but possibly very small)
observed probability of nondeterminism.  Our 12 hour run identified
all sources of nondeterminism successfully, according to a series of
48 hour runs performed on the version of the harness we modified to
remove nondeterminism.  We determined that the mean time to find all
the sources of nondeterminism and produce minimal tests 3.2
hours, which is not trivial, but also, for this purpose, not excessive.
